%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{Kyle Hershey} % Your name
\address{2296 Long Ave.\\ St. Paul, MN 55114} % Your address
\address{(608)~$\cdot$~345~$\cdot$~8595 \\ kwhershey@gmail.com} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
{\bf University of Minnesota} \hfill {\em August 2013-Present} \\
Ph.D. in Materials Science \& Engineering \\
Profesor Russell J. Holmes Research Group \\
Dow Chemical Company University Partnership Program Scholar

{\bf Coe College} \hfill {\em June 2013} \\ 
B.A. in Phyisics, Mathematics, and Computer Science \& Engineering \\
Member of Phi Beta Kappa\\
Member of Sigma Pi Sigma\\
Overall GPA: 3.927 

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Research Experience}

\begin{rSubsection}{University of Minnesota, Materials Science \& Engineering}{July 2013-Present}{Graduate Student}{Minneapolis, MN}

\item {\em Transient and Lifetime Dynamics of Organic Light Emitting Devices}

\item PI: Prof. Russell Holmes
\item Fabrication and testing of OLEDs
\item Device architecture optimization
\item Software development for device analysis software
\item Created perminant optical setups for Transient Photoluminescence and Electroluminescence studies
\item Model development for fitting experimental data of transient and steady-state electroluminescence
\item Optical, Theoretical, hardware and software development for unique OLED lifetime testing setup
\item Database setup for storing test data and data analysis
\item Multiplexing of testing setup for OLED lifetime
\item Extensive use of VISA command library and Serial communication for software connection to testing equipment
\item Advised High School research assistants on optically pumped laser development

\end{rSubsection}

%-----------------------------------------------

\begin{rSubsection}{Northwester University, Materials Science Department}{June 2012 - August 2012}{REU Student}{Evanston, IL}

\item {\em Field Enhancement Due to Plasmonic Nanostructures}

\item PI: Prof. George Schatz, Northwestern University, Chemistry 
\item Mentor: Montacer Dridi, Graduate student, Northwestern University, Chemistry 
\item Computational simulation of electromagnetic field enhancement near the surface of gold cylindrical dimers
\item Finite-difference time domain method simulation 
\item Constant transverse wavenumber spectral FDTD with periodic boundary conditions 
\item Cluster computing on Northwestern's high performance computing system - {\em Quest}
\item Software used: Fedora, Matlab, Emacs, Vim, Moab Cluster Suite, SSH, SCP
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Rockwell Collins, Inc., Advanced Technology Center, Microelectroncs Packaging Unit}{June 2011-August 2011}{Summer Intern}{Cedar Rapids, IA}
\item Microelectroncs die attach process development
\item Mentor: Guy Smith, Sr. Mechanical Engineer, Rockwell Collins, Inc.
\item Experience with: Class 10000 clean room, chip bonder, wire bonding, stud bumping, plating bahts, TLP bonding, AUSn eutectic bonding, solder bumping, BGA attachment, cross sectional die analysis
\item Composed internal documentation on  No Clean microelectronics die attachment and Transient Liquid Phase bonding
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Coe College}{June 2010-August 2010}{REU Student}{Cedar Rapids, IA}
\item PI: Prof. James Cottingham, Coe College, Physics 
\item Examined the effects of the vibrations in the pipe walls of free-reed wind instruments
\item Materials measurements of density and Young's modulus of bamboo pipes
\item Equipment used: FFT spectrum analyzer, Frequency generator, EDX with SEM
\item Theoretical modeling with Matlab and Mathematica
\item Presentation: {\em Material Properties of Pipes and Reeds from the Souteas Asian Khaen, Acoustics Society of America, May 2011, Seattle, WA}
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%PUBLICATIONS SECTION	
%----------------------------------------------------------------------------------------

\begin{rSection}{Publications}
\item {\em Blue-Emitting Arylalkynyl Naphthalene Derivatives via a Hexadehydro-Diels-Alder Cascade Reaction}, F Xu, KW Hershey, RH Holmes, TR Hoye. Journal of the American Chemical Society 138 (39), 12739-12742
\item {\em Unified Analysis of Transient and Steady-State Electrophosphorescence Using Exciton and Polaron Dynamics Modeling}, KW Hershey, RJ Holmes. Journal of Applied Physics 120 (19), 195501
\item {\em Matierial Properties of Pipes of Reeds From the Southeast Asian Khaen}, KW Hershey, JP Cottingham. Journal of the Acoustics Society of America, 129 (4) 2520

\end{rSection}

%----------------------------------------------------------------------------------------
%PRESENTATIONS SECTION	
%----------------------------------------------------------------------------------------

\begin{rSection}{Presentations}
\item {\em Material Properties of Pipes and Reeds from the Southeast Asian Khaen}, Sigma Pi Sigma Quadrennial Physics Congress. Poster. Orlando, FL. 2012.
\item {\em Material Properties of Pipes and Reeds from the Southeast Asian Khaen}, Acoustical Society of America National Meeting. Talk. Seattle, WA. May 2011 
\item {\em Transient Analysis of Organic Light-emitting Devices}, UMN IPrime. Poster. Minneapolis, MN. May 2015 
\item {\em Modeling Exciton and Polaron Dynamics to Analyze OLED Behavior}, MRS Spring Conference. Talk. Phoenix, AZ. April 2016 
\item {\em Modeling Exciton and Polaron Dynamics to Analyze OLED Behavior}, UMN IPrime. Talk. Minneapolis, MN. June 2016 
\item {\em Connecting Transient and Steady-State Dynamics in Organic Light Emitting Devices}, UMN IPrime. Poster. Minneapolis, MN. June 2016 
\item {\em Decoupling Degradation Mechanisms During Lifetime Testing of Organic Light-Emitting Devices}, UMN IPrime. Talk. Minneapolis, MN. June 2017 
\item {\em Decoupling Degradation Mechanisms During Lifetime Testing of Organic Light-Emitting Devices}, UMN IPrime. Poster. Minneapolis, MN. June 2017 

\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Strengths}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} p{11cm} }
Lab Equipment & Thermal evaporation vacuum chamber, glovebox, spin coater, UV ozone, sonicator, pulse generator, Impedence spectrometer, frequency generator, optical microscope, SEM, ellipsometer, oscilloscope, FFT spectrometer, source meter, spectrometer, arduino, Pulsed and CW lasers \\
Computer Skills & Microsoft Office Suite, Matlab, Mathematica, Anaconda, Autodesk Inventor, AutoCAD, Solidworks, OriginLabs, Github, ChemDraw \\
Programming Languages & Python, C, C++, C\#, Objective C, Matlab, Tk graphics, National Instrument VISA command library, HTML, PHP \\
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
% HONORS	
%----------------------------------------------------------------------------------------

\begin{rSection}{Honors}

\item Eagle Scout (2008)
\item Dean's List, Coe College
\item Member of Sigma Pi Sigma Physics Honors Society (Inducted 2013)
\item Member of Phi Beta Kappa (Inducted 2013)
\item Member of the Materials Research Society (Inducted 2016)
\item University of Minnesota College of Science and Engineering Fellowship (2013-2014)

\end{rSection}


%----------------------------------------------------------------------------------------
% LEADERSHIP 
%----------------------------------------------------------------------------------------

\begin{rSection}{Leadership}

\item  Society of Physics Students Coe College Chapter President 2012-2013
\item  Coe College Physics Club - Treasurer 2011-2012, Vice President 2012-2013
\item Math Help Room Supervisor, Coe College 2012-2013
\item Academic Achievement Program Tutor (Physics, Math, Computer Science)
\item Advised High school research students, UMN, 2016
\item Advised Undergraduate research student, UMN, 2017

\end{rSection}





%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
